Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
Edits to Section 3

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem*{remark}{Remark}

@@

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that the Fictitious Play
  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?}. Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

  \fb{why symbol $=:$? is it a definition?}

@@

  \begin{theorem}[Existence of NE]
    Under assumption (II), namely that the payoff function achieves a bilinear property, a
    Nash equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
  \end{theorem}

  \begin{theorem}
    There exists a path $m$ which satisfies the property that, for all agents $\mu$, $m^\mu \in
    BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
    \fb{why parameter $t$ if it does not appear anywhere in the statement?}
  \end{theorem}

@@

  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality \fb{which inequality?} yields that, for all agents $\mu$,
%
  \begin{equation} 
    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
  \end{equation}

  which is precisely the Nash equilibrium condition (Def.~\ref{def::NE}) in the NA game. This leads to the next result
%
  \begin{corollary} \label{thm::NACTFPtoNE}
    With the additional assumption that $w^{\mu \mu} = 0$ for all agents $\mu$, all zero-sum NA games have the property that any NA-CTFP path converges to the set of Nash Equilibria.
  \end{corollary}

>>>>

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem*{remark}{Remark}

@@

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that the Fictitious Play
  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?} \ah{So the existence of the NE and the FP dynamic are independent of one another. The NE is a property of the game only, whereas FP is a separate differential equation (12 in the supplementary material). Whilst it is intuitive that the solutions to (S12) exists, on a technical sense we still have to prove it.}. Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

@@

  \begin{lemma}[Existence of NE]
    Under assumption (II), namely that the payoff function achieves a bilinear property, a
    Nash equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
  \end{lemma}

  \begin{lemma}
    There exists a path $m(t)$ which satisfies the property that, for all agents $\mu$, $m^\mu(t) \in
    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all $t \geq 1$.
  \end{lemma}

@@

  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the fixed point corresponds to an NE. In particular Eqn. (26) in the supplementary materal corresponds to the NE condition when $w^{\mu \mu} = 0$. This leads to the next result.
%
  \begin{corollary} \label{thm::NACTFPtoNE}
    With the additional assumption that $w^{\mu \mu} = 0$ for all agents $\mu$, all zero-sum NA games have the property that any NA-CTFP path converges to the set of Nash Equilibria.
  \end{corollary}
